resevol: an R package for spatially explicit models of pesticide resistance given evolving pest genomes

### 2022-06-15 notebook/index.Rmd
I believe that I have now implemented the crop change using matrices, as introduced in Issue #43 -- the pesticide needs to be changed now too, and it absolutely must be tested @bradduthie -- make sure that the landscape values are accurate during the rotation

   - **JAN** [06](#u-06-JAN-2022)

@@

@@

```{r, echo = FALSE}
library(helicoverpa);
gmt       <- matrix(data = 0, nrow = 2, ncol = 2);
gmt[1, 1] <- 1;
gmt[2, 2] <- 1;
gmt[1, 2] <- -0.5;
gmt[2, 1] <- -0.5;
```

>>>>

   - **JUN** [13](#u-13-JUN-2022)
   - **JAN** [06](#u-06-JAN-2022)

@@

> <a name="u-13-JUN-2022">Update: 13 JUN 2022</a>

As I prepare the pre-print and software note for the resevol package, I am thinking that might be worth doing just a bit more coding so that the publication can include four more features:

1. **More explicit crop and pesticide rotation**, as mentioned in [Issue #43](https://github.com/bradduthie/resevol/issues/43). I think that this would be fairly easy to implement and worth the time. Currently, the `run_farm_sim` argument `crop_rotation_type` accepts either 1 or a 2. A 1 results in no rotation of crops on the landscape, and a 2 results in a random transition between types. I think that a custom transition matrix should be possible to insert, whereby each element should specify the probability of transitioning from crop *i* (row) to crop *j* (column). In the simplest case (e.g., could be `crop_rotation_type = 3`), this could just be a binary matrix that forms a cyclical graph. The current options 1 and 2 could even be subsumed in the transition matrix.
2. **Allow custom landscapes.** I think that this should be possible by allowing users to put their own matrix in a function, with numbers on the matrix representing different farms (integers greater than zeros) or public land (zeros). A new `custom_landscape` function could check this matrix, then use it as the top layer of an array.
3. **Custom plotting functions.** This one is tricky given the flexibility of simulations and therefore the complexity of the output, but it might be worth including at least some basic plotting functions, or summary functions.
4. **Simulated annealing algorithm** for the `mine_gmatrix` option. This could be fairly easy to implement, and for some cases might actually find genome solutions faster than the evolutionary algorithm.

My hope is that these different tasks could be done fairly quickly, and that they will make writing up the paper go more smoothly.

@@

```{r, echo = FALSE}
library(resevol);
gmt       <- matrix(data = 0, nrow = 2, ncol = 2);
gmt[1, 1] <- 1;
gmt[2, 2] <- 1;
gmt[1, 2] <- -0.5;
gmt[2, 1] <- -0.5;
```

### 2022-06-15 notebook/ms/ms.Rmd
I believe that I have now implemented the crop change using matrices, as introduced in Issue #43 -- the pesticide needs to be changed now too, and it absolutely must be tested @bradduthie -- make sure that the landscape values are accurate during the rotation

- We want to model evolution of pesticide resistance across heterogenous landscape
- Track entire genomes, traits, and yield over time and across space
- Use covarying traits from `mine_gmatrix` to make evolving pests
- Options for 10 crops and 10 pesticides simultaneously, and rotation
- Function `run_farm_sim` runs simulations

@@

- Example of evolving species with different crop and pesticide appications

>>>>

- We want to model evolution of pesticide resistance across heterogenous landscape
- Track entire genomes, traits, and yield over time and across space
- Use covarying traits from `mine_gmatrix` to make evolving pests
- Options for 10 crops and 10 pesticides simultaneously, and rotation
- Function `run_farm_sim` runs simulations. Note unusual timing structure

@@

- Example of evolving species with different crop and pesticide applications
